Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-16 paper/paper.tex
bis

Convolving the wavelets in this filterbank with an input waveform $\boldsymbol{x}\in\mathbf{L}^2(\mathbb{R}$, followed by an application of the pointwise complex modulus, yields the wavelet scalogram
\begin{equation}
\mathbf{U_1}\boldsymbol{x}(t,\log_2\lambda) =
\big\vert
\boldsymbol{x}
\ast
\boldsymbol{\psi}_{\lambda}
\big\vert(t)
=
\left\vert
\int_{\mathbb{R}}
\boldsymbol{x}(t^{\prime})
\,
\boldsymbol{\psi}_{\lambda} (t - t^{\prime})
\;
\mathrm{d}{t^\prime}
\right\vert,
\end{equation}
indexed by time $t$ and log-frequency $\log_2\lambda$.
Then, we define a two-dimensional Morlet wavelet $\boldsymbol{\Psi}$, taking a spectrotemporal pair $(t, \log_2 \lambda)$ as input:
\begin{equation}
\Psi : (t,\log_2 \lambda) \longmapsto 
\exp\left(-\dfrac{t^2+(\log_2 \lambda)^2}{2\sigma_{\Psi}^2}\right) 
\Big[ \exp\big(2\pi \mathrm{i} (t + \log_2 \lambda)\big) - \kappa_{\Psi} \Big].
\end{equation}
In the equation above, the Gaussian width $\sigma_{\Psi}$ is chosen so that the quality factor of the Morlet wavelet $\Psi$ is equal to $1$, both over the time dimension and over the log-frequency dimension.
Furthermore, the corrective term $\kappa_{\Psi}$ ensures that $\boldsymbol{\Psi}$ has a null average over $\mathbb{R}^2$, similarly to Equation \ref{eq:psi}.

>>>>

Convolving the wavelets in this filterbank with an input waveform $\boldsymbol{x}\in\mathbf{L}^2(\mathbb{R}$, followed by an application of the pointwise complex modulus, yields the wavelet scalogram
\begin{equation}
\mathbf{U_1}\boldsymbol{x}(t,\log_2\lambda) =
\big\vert
\boldsymbol{x}
\ast
\boldsymbol{\psi}_{\lambda}
\big\vert(t)
=
\left\vert
\int_{\mathbb{R}}
\boldsymbol{x}(t^{\prime})
\,
\boldsymbol{\psi}_{\lambda} (t - t^{\prime})
\;
\mathrm{d}{t^\prime}
\right\vert,
\end{equation}
indexed by time $t$ and log-frequency $\log_2\lambda$.
Then, we define a two-dimensional Morlet wavelet $\boldsymbol{\Psi}$, taking a spectrotemporal pair $(t, \log_2 \lambda)$ as input:
\begin{equation}
\Psi : (t,\log_2 \lambda) \longmapsto 
\exp\left(-\dfrac{t^2+(\log_2 \lambda)^2}{2\sigma_{\Psi}^2}\right) 
\Big[ \exp\big(2\pi \mathrm{i} (t + \log_2 \lambda)\big) - \kappa_{\Psi} \Big].
\end{equation}
In the equation above, the Gaussian width $\sigma_{\Psi}$ is chosen so that the quality factor of the Morlet wavelet $\Psi$ is equal to $1$, both over the time dimension and over the log-frequency dimension.
Furthermore, the corrective term $\kappa_{\Psi}$ ensures that $\boldsymbol{\Psi}$ has a null average over $\mathbb{R}^2$, similarly to Equation \ref{eq:psi}.
Following the terminology of spectrotemporal receptive fields (STRF, see \lnameref{sec:soa} section), we define a two-dimensional wavelet filterbank of the form:
\begin{equation}
\mathbf{\Psi}_{\alpha,\beta} : (t, \log_2 \lambda) \longmapsto
\mathbf{\Psi}\big(\alpha t, \beta \log_2 \lambda \big),
\end{equation}
where $\alpha$ is a temporal modulation rate and $\beta$ is a temporal modulation scale.

While $\alpha$ is measured in Hertz and is strictly positive, $\beta$ is measured in cycles per octaves and may take positive as well as negative values.
Both $\alpha$ and $\beta$ are discretized by geometric progressions of common ratio equal to $2$.
Furthermore, the edge case $\beta=0$ corresponds to $\mathbf{\Psi}_{\alpha,\beta}$ being a Gaussian low-pass filter over the log-frequency dimension, while remaining a Morlet band-pass filter of center frequency $\alpha$ over the time dimension.

% TODO define U2.
% Briefly define S2.

In comparison with the representation known as ``full cortical model'' \cite{patil2012ploscompbiol}, joint time--frequency scattering enjoys a thirty-fold reduction in dimensionality while covering a time span that is four times larger (1000 ms) and an acoustic bandwidth that is also four times larger (0--16 kHz).
We refer to \cite{anden2019tsp} for more details on the implementation of joint time--frequency scattering.
